\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-11 paper.qmd
explanation of binning

We define the function $u: \mathbb{R}^{n\times 2} \rightarrow \mathbb{R}^{m\times 2}$, which generates the model by assigning the points to bin centroids.

For the $i^{th}$ point, $u(i) = \arg\min_{j = 1, \dots, b} \sqrt{(y_{i1} - C^{(2)}_{j1})^2 + (y_{i2} - C^{(2)}_{j2})^2}$, and falls in $H_h = \{i| u(i) = h\}$.

When $k = 2$, the hexagonal bin centroid is one representation of a bin (@fig-NLDR-scurve (c)). Additionally, it can be the mean of the points within each hexagon.

>>>>

Observations are grouped into bins based on their nearest centroid. This can be defined using the function $u: \mathbb{R}^{n\times 2} \rightarrow \mathbb{R}^{m\times 2}$, where
$u(i) = \arg\min_{j = 1, \dots, b} \sqrt{(y_{i1} - C^{(2)}_{j1})^2 + (y_{i2} - C^{(2)}_{j2})^2}$, mapping observation $i$ into $H_h = \{i| u(i) = h\}$.

When $k = 2$, the hexagonal bin centroid is used (@fig-NLDR-scurve (c)). Any measure of center, such as a mean or weighted mean of the points within each hexagon, could be used to represent the hexagon.

### 2024-06-11 paper.tex
explanation of binning

We define the function
\(u: \mathbb{R}^{n\times 2} \rightarrow \mathbb{R}^{m\times 2}\), which
generates the model by assigning the points to bin centroids.

For the \(i^{th}\) point,
\(u(i) = \arg\min_{j = 1, \dots, b} \sqrt{(y_{i1} - C^{(2)}_{j1})^2 + (y_{i2} - C^{(2)}_{j2})^2}\),
and falls in \(H_h = \{i| u(i) = h\}\).

When \(k = 2\), the hexagonal bin centroid is one representation of a
bin (Figure~\ref{fig-NLDR-scurve} (c)). Additionally, it can be the mean
of the points within each hexagon.

>>>>

Observations are grouped into bins based on their nearest centroid. This
can be defined using the function
\(u: \mathbb{R}^{n\times 2} \rightarrow \mathbb{R}^{m\times 2}\), where
\(u(i) = \arg\min_{j = 1, \dots, b} \sqrt{(y_{i1} - C^{(2)}_{j1})^2 + (y_{i2} - C^{(2)}_{j2})^2}\),
mapping observation \(i\) into \(H_h = \{i| u(i) = h\}\).

When \(k = 2\), the hexagonal bin centroid is used
(Figure~\ref{fig-NLDR-scurve} (c)). Any measure of center, such as a
mean or weighted mean of the points within each hexagon, could be used
to represent the hexagon.
